---
title: "Diversionary_feeding"
date: "2024-03-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(GGally)
library(rjags)
library(coda)
library(MCMCvis)
library(HDInterval)
library(stringr)
library(cowplot)
library(ggmcmc)
library(ggbreak)
library(hrbrthemes)
library(MetBrewer)
library(jpeg)
library(patchwork)
```

# Introduction

In this model, we import the data and estimate depredations before and after the use of diversionary feeding. We used zero inflation to account for non-detected (aka reported or verified losses). Because there was the outlying question of whether the reduction could be attributed to temporal changes in prey vulnerability, we ran the subset model to see if there were any differences. 

```{r, warning = FALSE}
# load data
load('div_feeding_data.Rdata') # main dataset
load('div_feeding_data_sub.Rdata') # sub model of prey

ggpairs(dat, c(11:13)) # check correlation of detection covariates
ggpairs(dat, c(7,14,15)) # check correlation of depredation covariates


#scale covariates for detection
dat$forest_scaled = scale(dat$forest,center=TRUE, scale=TRUE)
dat$slope_scaled = scale(dat$slope,center=TRUE, scale=TRUE)
dat$roads_scaled = scale(dat$roads_area,center=TRUE, scale=TRUE)

#scale covariates for depredation
dat$Size_scaled = scale(dat$Size,center=TRUE, scale=TRUE)
dat$prey_scaled = scale(dat$prey,center=TRUE, scale=TRUE)
dat$cattle_scaled = scale(dat$cattle,center=TRUE, scale=TRUE)

```

# Prepare Jags model

```{r, warning = FALSE}

## settings just to try it. The whole script takes ~6 mins with these settings
n.adapt = 2500
n.update = 1000
n.iter = 10000
n.thin = 2

## settings for actual model. The script will take ~1.5 hours with these settings
#n.adapt = 100000
#n.update = 10000
#n.iter = 250000
#n.thin = 5

# initial values for MCMC chains
inits = list(
  list(b1 = 0, b2 = .01, b3 = 1.6,
       ba1 = 0, ba2 = .01, ba3 = 1.6,
       a1 = .75, a2 = .5, a3 = .1),
  list(b1 = 2, b2 = .0005, b3 = .06,
       ba1 = 2, ba2 = .0005, ba3 = .06,
       a1 = .9, a2 = .005, a3 = 10),
  list(b1 = 0, b2 = 1, b3 = 1.6,
       ba1 = 0, ba2 = 1, ba3 = 1.6, 
      a1 = 0, a2 = 1, a3 = .06),
  list(b1 = .001, b2 = 2.5, b3 = -1.3,
       ba1 = .001, ba2 = 2.5, ba3 = -1.3,
       a1 = -.8, a2 = -1, a3 = -.06))

#create regional intercept (NM is 2, AZ is 1) 
dat <- dat %>%
  mutate(graz1 = ifelse(graz ==0,1,2))

Mod <- dat # conserve original data file
Mod$new = Mod$Before_3months + Mod$After_3months

# Calculate z-value for zero inflation 
Mod <- Mod %>%
  mutate(Z = ifelse(new == 0,0,1))

# data list for JAGS
D = list(
  Yb = Mod$Before_3months,
  Ya = Mod$After_3months,
  pSize = as.double(Mod$Size_scaled), 
  prey = as.double(Mod$prey_scaled),
  cattle = as.double(Mod$cattle_scaled),
  n = length(Mod$Pack),
  s = as.double(Mod$slope_scaled),
  f = as.double(Mod$forest_scaled),
  r = as.double(Mod$roads_scaled),
  St = Mod$graz1,
  z = Mod$Z)


```


# Model

This is the full model to be run in jags. 
```{r}
set.seed(10)
sink("Mexwolf_poisson.R")
cat("
model {
  #priors
  # detection process
   for (j in 1:2){
   a0[j]~dnorm(0,1/1000)
  }
  a1 ~ dlogis(0,1)
  a2 ~ dlogis(0,1)
  a3 ~ dlogis(0,1)
  # depredation (before) process
  for (j in 1:2){
   b0[j]~dnorm(0,1/1000)
  }
  b1 ~ dnorm(0,1/1000)
  b2 ~ dnorm(0,1/1000)
  b3 ~ dnorm(0,1/1000)
  # depredation (after) process
  for (j in 1:2){
   ba0[j]~dnorm(0,1/1000)
  }
  ba1 ~ dnorm(0,1/1000)
  ba2 ~ dnorm(0,1/1000)
  ba3 ~ dnorm(0,1/1000)


#Likelihood for depredation encounter process
for (i in 1:n) {
    logit(p[i]) <- a0[St[i]] + a1 * s[i] + a2 * f[i]  + a3 * r[i]
    z[i] ~ dbern(p[i])
    sim_z[i] ~ dbern(p[i])
}    

# likelihood for depredations before
for (i in 1:n) {
    Yb[i] ~ dpois(mu[i]*z[i])
        mu[i] <- exp(b0[St[i]] + b1 * pSize[i] * pSize[i] + b2 * prey[i] + b3 * cattle[i])
    sim_depredations[i] ~ dpois(mu[i]*z[i])
} 

# likelihood for depredations after
for (i in 1:n) {
    Ya[i] ~ dpois(mu1[i]*z[i])
        mu1[i] <- exp(ba0[St[i]] + ba1 * pSize[i] * pSize[i] + ba2 * prey[i] + ba3 * cattle[i])
    sim_depredations1[i] ~ dpois(mu1[i]*z[i])
}  

#get bayesian p-values for depredation and detection model
data_mean <- mean(Yb[])
sim_mean <- mean(sim_depredations[])
pvalue_mean_dep <- step(sim_mean-data_mean)

data_mean1 <- mean(Ya[])
sim_mean1 <- mean(sim_depredations1[])
pvalue_mean_dep_aft <- step(sim_mean1-data_mean1)

data_mean_z <- mean(z[])
sim_mean_z <- mean(sim_z[])
pvalue_mean_z <- step(sim_mean_z - data_mean_z)

pmean <- mean(p[])
sumbef <- sum(mu[])
sumaft <- sum(mu1[])
reduc <- sum(mu[])-sum(mu1[])
diff <- (1-sum(mu1[])/sum(mu[]))
mu_mean <- mean(mu[])
mu1_mean <- mean(mu1[])
means <- mean(mu[])-mean(mu1[])
}
", fill = TRUE)

jm = jags.model("Mexwolf_poisson.R", 
                data = D, 
                inits = inits, 
                n.chains = length(inits), 
                n.adapt = n.adapt)

update(jm, n.iter = n.update)

zm = coda.samples(jm, variable.names = c("diff",
                                         "reduc",
                                         "means",
                                         "sumbef",
                                         "sumaft",
                                         "mu_mean",
                                         "mu1_mean",
                                         "pmean",
                                         "p",
                                         "mu",
                                         "mu1",
                                         "b0","b1","b2","b3", 
                                         "a0","a1","a2","a3",
                                         "ba0","ba1","ba2","ba3",
                                         "pvalue_mean_dep",
                                         "pvalue_mean_dep_aft",
                                         "pvalue_mean_z"),
                                          n.iter = n.iter, 
                                          n.thin = n.thin)

Reduction <- MCMCsummary(zm, params = c("diff", "reduc","means", "sumbef", "sumaft", "pmean")) #  % reduction

Reduction$se <- Reduction$sd / sqrt(73)

means <- MCMCsummary(zm, params = c("mu_mean", "mu1_mean"))

means$se <- means$sd / sqrt(73)
  
# Caterpillar plots

MCMCplot(zm,params=c("b0", "b1", "b2", "b3"), 
         main = "Depredations before div feeding")
MCMCplot(zm,params=c("a1", "a2", "a3"), 
         main = "Factors affecting detection before")

MCMCplot(zm,params=c("ba0", "ba1", "ba2", "ba3"), 
         main = "Depredations after div feeding")
MCMCplot(zm,params=c("mu"), rank = TRUE, horiz = FALSE, main = "Estimated depredations before")
MCMCplot(zm,params=c("mu1"), rank = TRUE, horiz = FALSE, main = "Estimated depredations after")

# Assess traceplots
MCMCtrace(zm, params="p", pdf = F)
MCMCtrace(zm, params="mu", pdf = F)
MCMCtrace(zm, params="mu1", pdf = F)

# Get Bayesian p-values
pvalue_mean_dep <- round(MCMCpstr(zm, params = c("pvalue_mean_dep"),
func = mean)$pvalue_mean[1], 2)

pvalue_mean_dep_aft <- round(MCMCpstr(zm, params = c("pvalue_mean_dep_aft"),
func = mean)$pvalue_mean[1], 2) 

pvalue_mean_z <- round(MCMCpstr(zm, params = c("pvalue_mean_z"),
func = mean)$pvalue_mean[1], 2)

```

## Subset model
This model is to compare the group that does not have elk calving in the post-treatment period.  
```{r}

#scale covariates for detection
sub$forest_scaled = scale(sub$forest,center=TRUE, scale=TRUE)
sub$slope_scaled = scale(sub$slope,center=TRUE, scale=TRUE)
sub$roads_scaled = scale(sub$roads_area,center=TRUE, scale=TRUE)

#scale covariates for depredation
sub$Size_scaled = scale(sub$Size,center=TRUE, scale=TRUE)
sub$prey_scaled = scale(sub$prey,center=TRUE, scale=TRUE)
sub$cattle_scaled = scale(sub$cattle,center=TRUE, scale=TRUE)

submod <- sub
submod$new = submod$Before_3months + submod$After_3months

# Calculate z-value for zero inflation 
submod <- submod %>%
  mutate(Z = ifelse(new == 0,0,1))

submod <- submod %>%
  mutate(graz1 = ifelse(graz ==0,1,2))

# list for JAGS
Dsub = list(
  Yb = submod$Before_3months,
  Ya = submod$After_3months,
  pSize = as.double(submod$Size_scaled), 
  prey = as.double(submod$prey_scaled),
  cattle = as.double(submod$cattle_scaled),
  n = length(submod$Pack),
  s = as.double(submod$slope_scaled),
  f = as.double(submod$forest_scaled),
  r = as.double(submod$roads_scaled),
  St = submod$graz1,
  z = submod$Z)

set.seed(10)
sink("Mexwolf_poisson.R")
cat("
model {
  #priors
  # detection process
   for (j in 1:2){
   a0[j]~dnorm(0,1/1000)
  }
  a1 ~ dlogis(0,1)
  a2 ~ dlogis(0,1)
  a3 ~ dlogis(0,1)
  # depredation (before) process
  for (j in 1:2){
   b0[j]~dnorm(0,1/1000)
  }
  b1 ~ dnorm(0,1/1000)
  b2 ~ dnorm(0,1/1000)
  b3 ~ dnorm(0,1/1000)
  # depredation (after) process
  for (j in 1:2){
   ba0[j]~dnorm(0,1/1000)
  }
  ba1 ~ dnorm(0,1/1000)
  ba2 ~ dnorm(0,1/1000)
  ba3 ~ dnorm(0,1/1000)


#Likelihood for depredation encounter process
for (i in 1:n) {
    logit(p[i]) <- a0[St[i]] + a1 * s[i] + a2 * f[i]  + a3 * r[i]
    z[i] ~ dbern(p[i])
    sim_z[i] ~ dbern(p[i])
}    

# likelihood for depredations before
for (i in 1:n) {
    Yb[i] ~ dpois(mu[i]*z[i])
        mu[i] <- exp(b0[St[i]] + b1 * pSize[i] * pSize[i] + b2 * prey[i] + b3 * cattle[i])
    sim_depredations[i] ~ dpois(mu[i]*z[i])
} 

# likelihood for depredations after
for (i in 1:n) {
    Ya[i] ~ dpois(mu1[i]*z[i])
        mu1[i] <- exp(ba0[St[i]] + ba1 * pSize[i] * pSize[i] + ba2 * prey[i] + ba3 * cattle[i])
    sim_depredations1[i] ~ dpois(mu1[i]*z[i])
}  

#get bayesian p-values for depredation and detection model
data_mean <- mean(Yb[])
sim_mean <- mean(sim_depredations[])
pvalue_mean_dep <- step(sim_mean-data_mean)

data_mean1 <- mean(Ya[])
sim_mean1 <- mean(sim_depredations1[])
pvalue_mean_dep_aft <- step(sim_mean1-data_mean1)

data_mean_z <- mean(z[])
sim_mean_z <- mean(sim_z[])
pvalue_mean_z <- step(sim_mean_z - data_mean_z)

pmean <- mean(p[])
sumbef <- sum(mu[])
sumaft <- sum(mu1[])
reduc <- sum(mu[])-sum(mu1[])
diff <- (1-sum(mu1[])/sum(mu[]))
mu_mean <- mean(mu[])
mu1_mean <- mean(mu1[])
means <- mean(mu[])-mean(mu1[])
}
", fill = TRUE)

jm_sub = jags.model("Mexwolf_poisson.R", 
                data = Dsub, 
                inits = inits, 
                n.chains = length(inits), 
                n.adapt = n.adapt)

update(jm_sub, n.iter = n.update)

zm_sub = coda.samples(jm_sub, variable.names = c("diff",
                                         "reduc",
                                         "means",
                                         "sumbef",
                                         "sumaft",
                                         "mu_mean",
                                         "mu1_mean",
                                         "p",
                                         "mu",
                                         "mu1",
                                         "b0","b1","b2","b3",  
                                         "a0","a1","a2","a3",
                                         "ba0","ba1","ba2","ba3",
                                         "pvalue_mean_dep",
                                         "pvalue_mean_dep_aft",
                                         "pvalue_mean_z"),
                                          n.iter = n.iter, 
                                          n.thin = n.thin)

Reduction_sub <- MCMCsummary(zm_sub, 
                             params = c("diff", "reduc","means", 
                                        "sumbef", "sumaft")) 

Reduction_sub$se <- Reduction_sub$sd / sqrt(47)

p_sub <- MCMCsummary(zm_sub, params = "p")

# Caterpillar plots

MCMCplot(zm_sub,params=c("b0", "b1", "b2", "b3"), 
         main = "Depredations before div feeding")
MCMCplot(zm_sub,params=c("a1", "a2", "a3"), 
         main = "Factors affecting detection before")

MCMCplot(zm_sub,params=c("ba0", "ba1", "ba2", "ba3"), 
         main = "Depredations after div feeding")
MCMCplot(zm_sub,params=c("mu"), rank = TRUE, 
         horiz = FALSE, main = "Estimated depredations before")
MCMCplot(zm_sub,params=c("mu1"), rank = TRUE, 
         horiz = FALSE, main = "Estimated depredations after")

# Assess traceplots
MCMCtrace(zm_sub, params="p", pdf = F)
MCMCtrace(zm_sub, params="mu", pdf = F)
MCMCtrace(zm_sub, params="mu1", pdf = F)

```


## Extract estimates for the full model

```{r}
x <-MCMCsummary(zm, params = "p") #  p summary values
y <-MCMCsummary(zm, params = "mu") #  before div mu summary values
z <-MCMCsummary(zm,params = "mu1") #  after div mu summary values

colnames(x)[c(1, 2, 3, 5)] <- c("p", "p_sd", "p_lci", "p_uci")
x$SEp <- x$p_sd / sqrt(length(x)) # calculate SE from SD

colnames(y)[c(1, 2, 3, 5)] <- c("dep_before", "dep_before_sd", "dep_before_lci", "dep_before_uci")
y$SEdep <- y$dep_before_sd / sqrt(length(y))

colnames(z)[c(1, 2, 3, 5)] <- c("dep_after", "dep_after_sd", "dep_after_lci", "dep_after_uci")
z$SEdep1 <- z$dep_after_sd / sqrt(length(z))

BM <- Mod %>%
  arrange(OBJECTID_1)


BM <- BM [,c(1,3,6)]
results<-bind_cols(BM,x,y,z) # bind together detection, depredation and original data


# predictor estimates w/ 95% and 75% BCI
betas95 <- MCMCsummary(zm, params = c("b0", "b1", "b2", "b3"))
betas75 <- MCMCsummary(zm, params = c("b0", "b1", "b2", "b3"), probs = c(.125,.875))

betasafter <- MCMCsummary(zm, params = c("ba0", "ba1", "ba2", "ba3"))
betasafter75 <- MCMCsummary(zm, params = c("ba0", "ba1", "ba2", "ba3"), probs = c(.125,.875))
# alpha 
alphas_est <- MCMCsummary(zm, params = c("a0", "a1", "a2", "a3"))
alphas75 <- MCMCsummary(zm, params = c("a0", "a1", "a2", "a3"), probs = c(.125,.875))

suppressWarnings(remove(x,y,Modbefore,z, inits, BM))

```


### Detection means and annual stats

```{r}
results <- as.data.frame(results)
p_means <- results %>%
  summarise(mean_p = mean(p), 
            lci = mean(p_lci),
            uci = mean(p_uci),
            se = mean(SEp)
            ) 

annual_det <- results %>%
  group_by(Year) %>%
  summarise(mean_p = mean(p), 
            lci = mean(p_lci),
            uci = mean(p_uci),
            se = mean(SEp))


ALL <- left_join(results, morts, by = c("Pack", "Year"))
ALL$Size <- dat$Size

ALL$FIN <- ALL$dep_after > ALL$dep_before

ALL <- ALL %>% filter(FIN == "TRUE")



```


# Visuals of the model

## Depredation
```{r}
mean_before <- mean(results$dep_before)
mean_after <- mean(results$dep_after)

means = coda.samples(jm, variable.names = c("mu_mean","mu1_mean"), 
                     n.iter = n.iter, n.thin = n.thin)
df_means <- ggs(means)
mu_bef <- df_means |> filter(Parameter == "mu_mean")
mu_af <- df_means |> filter(Parameter == "mu1_mean")
mean_before <- mean(mu_bef$value)
mean_after <- mean(mu_af$value)


densityNL <- ggplot()+
  geom_density(data = mu_bef, mapping =aes(x=value, fill = "Before",..scaled..),
               alpha=.85)+
  geom_density(data = mu_af,mapping =aes(x=value, fill = "After",..scaled..),
               alpha =.85)+
  geom_vline(xintercept = mean_before, color = "#99610a",lwd=2, linetype = 2)+
  geom_vline(xintercept = mean_after, color = "#6f948c",lwd=2, linetype = 2)+
  labs(x= "Depredations per pack-year", 
       y="Posterior density", 
       title = "(a)")+
  theme_half_open()+
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=15,face="bold"), 
        legend.position = "NONE")+
  scale_fill_manual(name='Estimates',
                     values=c("#6f948c","#99610a"))+
  xlim(0,3)+
  ylim(0,1)

### copy of the plot for the legend ####
densityWL <- ggplot()+
  geom_density(data = results, 
               mapping =aes(x=dep_before, 
                            fill = "Before",..scaled..), alpha=.9)+
  geom_density(data = results, 
               mapping =aes(x=dep_after, 
                            fill = "After",..scaled..), alpha =.9)+
  theme_half_open()+
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=15,face="bold"))+
  scale_fill_manual(name='Estimates',
                     values=c("#6f948c","#99610a"))

deplegend <- get_legend(densityWL+theme(legend.box.margin = margin(0, 0, 0, 12))
)

##### process data for yearly dep data ###########

yearly <- results %>%
  group_by(Year) %>%
  summarise(sumdep = sum(dep_before),
            se = sum(SEdep),
            lci = sum(dep_before_lci),
            uci = sum(dep_before_uci),
            type = "1")
yearly1 <- results %>%
  group_by(Year) %>%
  summarise(sumdep = sum(dep_after),
            se = sum(SEdep1),
            lci = sum(dep_after_lci),
            uci = sum(dep_after_uci),
            type = "2")

yearly <- bind_rows(yearly,yearly1)

dodge1<-position_dodge(width=.9)


yearly$type <- factor(yearly$type, levels = c("Before", "After"))

yearlyse <- ggplot(data = yearly)+
  geom_col(mapping = aes(x=Year,y=sumdep, fill = type), 
           color = "black", position=dodge1, alpha = 0.9)+
  geom_errorbar(aes(x = Year, ymin=sumdep - se ,ymax=sumdep + se , 
                                   fill = type), color = "#636363",
               lwd=.75,width=0.25,position=dodge1)+
  labs(y = "Depredations", fill = NULL)+
  scale_y_continuous(breaks = seq(0,30,5))+
  scale_fill_manual(labels = c("After", "Before"), 
                    values = c("#6f948c", "#99610a"))+
  theme_half_open()+
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=15,face="bold"),
        legend.position = "right")+
  scale_x_continuous(breaks = seq(2014,2021,1))

yearlyse
ggsave('Figure2_depredations_v2.jpg', dpi = 600, width = 10, height=8)


####### put it together ##############
plots <- plot_grid(densityNL, yearlyse, nrow =2, align = "hv")  
figure2<- suppressWarnings(plot_grid(plots,deplegend, ncol = 2, 
                    align = "hv",rel_widths = c(3, .4)))
figure2
#ggsave('Figure2_depredations.jpg', dpi = 600, width = 10, height=8)

# clean up environment
#suppressWarnings(rm(yearly_before, yearly_lci,yearly_uci, yearly_after, yearly_uci, yearly_lci,deplegend,dodge1,dodge2,plots,yearly,yearly_dat,densityWL,densityNL, yearly_se, yearly_se1))

```


## Caterpillar plots of betas

```{r}

betas75<- rownames_to_column(betas75, var = "Parameter")
betas95 <- rownames_to_column(betas95, var = "Parameter")

bbval <- left_join(betas95,betas75, by = "Parameter")

cat1 <- ggplot(bbval, aes(y = Parameter, x = mean.x))+
  geom_vline(xintercept = 0, color = "#999999", linetype =2, linewidth = 2)+
    geom_errorbarh(aes(xmin=`2.5%`, xmax=`97.5%`), 
                 height=0, color="#99610a", size = 1) +
  geom_errorbarh(aes(xmin=`12.5%`, xmax=`87.5%`), 
                 height=0, color="#99610a", size = 2) +
  geom_point(size = 5, alpha = 1)+
    aes(color = "(a) Depredation before", alpha = 1)+
  scale_color_manual(values = "#99610a")+
  theme_half_open()+
  scale_y_discrete(labels=c('New Mexico \nintercept',
                            'Arizona \nintercept',
                            'Minimum \npack size ', 
                            'Prey density',
                            'Annual live-\nstock density'))+
  scale_x_continuous(breaks=seq(-1.5,1.5,.5), limits = c(-1.5, 1.5))+
  labs(title = "(a) Before", 
       x = expression(beta*" coefficient"))+
    theme(axis.text=element_text(size=12),
        axis.title=element_text(size=15,face="bold"), 
        legend.position = "none",
        title = element_text(size = 20, face = "bold"))

betas75af<- rownames_to_column(betasafter, var = "Parameter")
betas95af <- rownames_to_column(betasafter75, var = "Parameter")

baval <- left_join(betas95af,betas75af, by = "Parameter")

cat2 <- ggplot(baval, aes(y = Parameter, x = mean.x))+
  geom_vline(xintercept = 0, color = "#999999", linetype =2, linewidth = 2)+
    geom_errorbarh(aes(xmin=`2.5%`, xmax=`97.5%`), 
                 height=0, color="#6f948c", size = 1) +
  geom_errorbarh(aes(xmin=`12.5%`, xmax=`87.5%`), 
                 height=0, color="#6f948c", size = 2) +
  geom_point(size = 5, alpha = 1)+
  aes(color = "(b) Depredation after", alpha = 1)+
  scale_color_manual(values = "#6f948c")+
  theme_half_open()+
  scale_y_discrete(labels=c('New Mexico \nintercept',
                            'Arizona \nintercept',
                            'Minimum \npack size ', 
                            'Prey density',
                            'Annual live-\nstock density'))+
  scale_x_continuous(breaks=seq(-1.5,1.5,.5), limits = c(-1.5, 1.5))+
  labs(title = "(b) After", 
       x = expression(beta*" coefficient"))+
    theme(axis.text=element_text(size=12),
        axis.title=element_text(size=15,face="bold"), 
        legend.position = "none",
        title = element_text(size = 20, face = "bold"))

plot_grid(cat1,cat2)

#ggsave('Figure3. Depredation covariates.jpg', dpi = 600, height =10, width = 20)



```

## Annual detection & alpha plot

```{r}
meandet <- p_means$mean_p # get mean probability of detection

figure4a <- ggplot(results, aes(x=Year,group=Year, y=p))+
  geom_boxplot(varwidth=T, fill = "#003455", alpha = .7)+
  geom_hline(yintercept = meandet, color = "red",linetype =2, lwd = 1)+
  theme_half_open()+
  labs(x="Year", y="Probability of detection", title = "(a)")+
  scale_x_continuous(breaks=seq(2014,2021,1))+
  scale_y_continuous(breaks = seq(.3,.8,.1), limits = c(.3, .8))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=15,face="bold"),
        title = element_text(size = 20, face = "bold"))


alphas_est<- rownames_to_column(alphas_est, var = "Parameter")
alphas75 <- rownames_to_column(alphas75, var = "Parameter")

alp <- left_join(alphas_est,alphas75, by = "Parameter")
alp <- alp[3:5,]

alpha_plot <- ggplot(alp, aes(y = Parameter, x = mean.x))+
  geom_vline(xintercept = 0, color = "#999999", linetype =2, linewidth = 2)+
    geom_errorbarh(aes(xmin=`2.5%`, xmax=`97.5%`), 
                 height=0, color="#003455", size = 1) +
  geom_errorbarh(aes(xmin=`12.5%`, xmax=`87.5%`), 
                 height=0, color="#003455", size = 2) +
  geom_point(size = 5, alpha = 1)+
    aes(color = "#003455", alpha = 1)+
  scale_color_manual(values = "#003455")+
  theme_half_open()+
  scale_y_discrete(labels=c('Slope', 'Forest\nCover', 'Roads'))+
  scale_x_continuous(breaks=seq(-1.5,1.5,.5), limits = c(-1.5, 1.5))+
  labs(title = "(b)", 
       x = expression(beta*" coefficient"))+
    theme(axis.text=element_text(size=12),
        axis.title=element_text(size=15,face="bold"), 
        legend.position = "none",
        title = element_text(size = 20, face = "bold"))


figure4 <- plot_grid(figure4a,alpha_plot, rel_widths = c(1,1.25))
figure4
#ggsave('Figure4.jpg', dpi = 600, width = 18, height=10)

```

